Determinism, Complexity, and Predictability in Computer Performance

### 2014-04-25 concl.tex
typo in concl

All of the experiments described in this paper involve a particular
physical system.  We chose that system because its behavior spans a
broad spectrum of classical time series patterns.  Since these
patterns (dynamical chaos, periodicities, noise, etc.) are generic, we
believe that our results will generalize beyond this particular
system.  Testing that claim with different examples is another
important next step---and one that will be critical to validating our
claims about the utility of the dashed line as a heuristic for
determining whether a particular forecast method is well-matched to a
particular task.  Of particular interest would be the class of
so-called \emph{hybrid systems}, which exhibit discrete transitions
between different continuous regimes---e.g., a lathe that has an
intermittent instability or traffic at an internet router, whose
characteristic normal traffic patterns shift radically during an
attack.  Effective modeling and prediction of these kinds of systems
effectively is quite difficult; doing so adaptively and
automatically---in the manner that is alluded to at the end of the
previous paragraph---would be an even more important challenge.

>>>>

All of the experiments described in this paper involve a particular
physical system.  We chose that system because its behavior spans a
broad spectrum of classical time series patterns.  Since these
patterns (dynamical chaos, periodicities, noise, etc.) are generic, we
believe that our results will generalize beyond this particular
system.  Testing that claim with different examples is another
important next step---and one that will be critical to validating our
claims about the utility of the dashed line as a heuristic for
determining whether a particular forecast method is well-matched to a
particular task.  Of particular interest would be the class of
so-called \emph{hybrid systems}, which exhibit discrete transitions
between different continuous regimes---e.g., a lathe that has an
intermittent instability or traffic at an internet router, whose
characteristic normal traffic patterns shift radically during an
attack.  Effective modeling and prediction of these kinds of systems
is quite difficult; doing so adaptively and automatically---in the
manner that is alluded to at the end of the previous paragraph---would
be an even more important challenge.
